Adolescent well-being in the digital age

### 2022-06-30 05-supp.Rmd
wip 2022-06-30

# Control analyses

@@

dat <- readRDS("data/data-all.rds")
```

@@

## Human development index

```{r}
itu <- read_rds("data/itu.rds")
itu %>%
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, hdi)) +
  scale_y_continuous(
    "Value",
    labels = ~percent(., .1),
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country)),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  facet_grid(
    ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    aspect.ratio = 1,
    legend.position = "none",
    panel.spacing.x = unit(4, "pt"),
    panel.spacing.y = unit(6, "pt"),
    axis.title.y = element_blank()
  )
```

@@

### Between-country associations

@@

### Within-country associations

@@

>>>>

# Supplemental analyses

```{r setup, include = FALSE}
library(lubridate)
library(scales)
library(broom)
library(patchwork)
library(spData)
library(tmap)
library(countrycode)
library(ggtext)
library(janitor)
library(kableExtra)
library(ggstance)
library(ggh4x)
library(mgcv)
library(tidyverse)

source("_common.R")

dat <- readRDS("data/data-all.rds")
itu <- read_rds("data/itu.rds")
```

## Control analyses

@@

```

@@

### Human development index

```{r}
itu %>%
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, hdi)) +
  scale_y_continuous(
    "Human Development Index",
    labels = ~percent(., .1),
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country)),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  facet_grid(
    ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    aspect.ratio = 1,
    legend.position = "none",
    panel.spacing.x = unit(4, "pt"),
    panel.spacing.y = unit(6, "pt")
  )
```

@@

#### Between-country associations

@@

#### Within-country associations

@@

## Maps

```{r}
itu <- read_rds("data/itu.rds") %>%
  select(
    region, country, year,
    Internet = internet,
    Mobile = mobile
  ) %>%
  pivot_longer(
    c(Internet, Mobile),
    names_to = "outcome", values_to = "val"
  )

d <- bind_rows(
  read_rds("data/gwp.rds"),
  read_rds("data/gbd.rds"),
  itu
)
```

Average well being and internet in each country

```{r}
x <- d %>% 
  mutate(outcome = if_else(str_detect(outcome, "_"), "Well-being", outcome)) %>% 
  filter(outcome %in% c("Well-being", "Internet")) %>% 
  group_by(outcome, country) %>% 
  summarise(val = mean(val, na.rm = TRUE)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = outcome, values_from = val)

map_internet <- world %>% 
  mutate(country = countryname(name_long)) %>% 
  inner_join(x) %>% 
  tm_shape() +
  tm_borders(lwd = .15)

tmap_mode(mode = "view")
pa <- map_internet +
  tm_fill(
    col = "Internet", 
    palette = "viridis", 
    style = "cont", 
    legend.reverse = TRUE
    )
pb <- map_internet +
  tm_fill(
    col = "Well-being", 
    palette = "viridis", 
    style = "cont", 
    legend.reverse = TRUE
    )
tmap_arrange(pa, pb, sync = TRUE)
```

## GBD metrics

While the Gallup data are (intended to be) representative of each country & year, there is more uncertainty in the GBD data. The latter are meta-analytic estimates produced by the IHME and as such can be inaccurate in some locations and or/years. Here, we compare the GBD self-harm indicator to CDC's self-injury data from <https://wisqars.cdc.gov>.

```{r}
# Load data sets
gbd <- read_rds("data/gbd.rds") %>% 
  filter(country == "US", outcome == "Selfharm") %>% 
  group_by(year, age) %>% 
  summarise(val = mean(val), se = mean(se)) %>% 
  filter(year > 2001)

cdc <- read_csv("data-raw/CDC/wisqars.csv") %>% 
  clean_names()
cdc <- cdc %>% 
  mutate(
    val = as.numeric(injuries) / as.numeric(population),
    se = as.numeric(standard_error) / as.numeric(population)
  ) %>% 
  select(
    year, 
    age = age_group,
    val, se
  ) %>% 
  mutate(
    age = str_replace(age, "-", " to ")
  )
```

```{r}
bind_rows(
  "IHME" = gbd,
  "CDC" = cdc,
  .id = "Source"
) %>% 
  drop_na(val) %>% 
  ggplot(aes(year, val, col = Source, fill = Source, group = Source)) +
  scale_y_continuous(
    "Rate",
    labels = ~percent(., .01),
    breaks = extended_breaks(5)
  ) +
  geom_ribbon(aes(ymin = val - se, ymax = val + se), col = NA, alpha = .2) +
  geom_line() +
  facet_wrap("age", ncol = 8) +
  theme(
    legend.position = "bottom",
    axis.title.x = element_blank()
  )
```
